Modeling Environmental Stochasticity

### 2022-04-22 notes/environmental stochasticity.Rmd

library(patchwork)
p0 + p1 + p2 + p3 &
  labs(y = ".fitted") &
  theme(legend.position = "none") &
  plot_annotation(title = "survival probability")
```

>>>>

library(patchwork)
p0 + p1 + p2 + p3 &
  labs(y = ".fitted") &
  theme(legend.position = "none") &
  plot_annotation(title = "survival probability") &
  ylim(0,1)
```
